# Figure 4

```{r, lib_comparison_setup}
libs <- c("PPV322", "PPV538")
sample_names <- c("Run X", "Run Y")
names(sample_names) <- libs
dummy_list <- as.list(1:2)
names(dummy_list) <- libs
sample_pwgs <- dummy_list
design_pwgs <- dummy_list
sample_barc <- dummy_list
design_barc <- dummy_list
for(lib in libs) {
  sample_pwgs[[lib]] <- read.csv(sprintf("../Data/%s/PooledWGSSampleReport.csv", lib), stringsAsFactors=FALSE)
  design_pwgs[[lib]] <- read.csv(sprintf("../Data/%s/PooledWGSDesignReport.csv", lib), stringsAsFactors=FALSE) %>%
    filter(DesignCategory == "edit") %>%
    mutate(
      OnyxEditReadCount = as.numeric(OnyxEditReadCount),
      TotalSpanningReadCount = as.numeric(TotalSpanningReadCount),
      FracOnyxEditReadCount = as.numeric(FracOnyxEditReadCount)
    ) %>%
    arrange(DesignId)
  sample_barc[[lib]] <- read.csv(sprintf("../Data/%s/BarcodeAmpliconSampleReport.csv", lib), stringsAsFactors=FALSE)
  design_barc[[lib]] <- read.csv(sprintf("../Data/%s/BarcodeAmpliconDesignReport.csv", lib), stringsAsFactors=FALSE) %>%
    filter(DesignCategory == "edit") %>%
    mutate(DesignFractionalAbundance=DesignFractionalAbundance/sum(DesignFractionalAbundance)) %>%
    arrange(DesignId)
}
S <- nrow(design_pwgs[[1]])

edit_repr_range <- 10^c(-1,2)
edit_fraction <- dummy_list
edit_results <- dummy_list
edit_beta_param <- dummy_list
edit_fig_lib_comparison <- dummy_list
design_repr_range <- 10^c(-2,1)
design_results <- dummy_list
design_beta_param <- dummy_list
design_fig_lib_comparison <- dummy_list
for(lib in libs) {
  # Designs
  design_results[[lib]] <- repr_hist_and_qq_plot(
    design_barc[[lib]]$DesignCount,
    sum(design_barc[[lib]]$DesignCount),
    repr_range=design_repr_range,
    var_type="Design"
  )
  design_beta_param[[lib]] <- get_beta_param(S, design_results[[lib]]$cv_bbinom_est)
  design_fig_lib_comparison[[lib]] <- design_results[[lib]]$fig_repr_hist +
    my_theme +
    labs(y="Reagent Count") +
    ggtitle(paste(sample_names[[lib]], ", Reagents", sep=""))
  # Edits
  edit_fraction[[lib]] <- sum(design_pwgs[[lib]]$FracOnyxEditReadCount)
  edit_results[[lib]] <- repr_hist_and_qq_plot(
    design_pwgs[[lib]]$OnyxEditReadCount,
    round(edit_fraction[[lib]] * design_pwgs[[lib]]$TotalSpanningReadCount),
    repr_range=edit_repr_range,
    var_type="Edit"
  )
  edit_beta_param[[lib]] <- get_beta_param(S, edit_results[[lib]]$cv_bbinom_est)
  edit_fig_lib_comparison[[lib]] <- edit_results[[lib]]$fig_repr_hist +
    my_theme +
    ggtitle(paste(sample_names[[lib]], ", Edits", sep=""))
}

m_screener <- S
m <- sort(c(m_screener, seq(100, 50000, length=200), 10^seq(1, 6, length=200)))
richness_data <- tibble(expand.grid(Cells=m, Sample=sample_names)) %>%
  inner_join(tibble(
    Sample=sample_names,
    EditFraction=unlist(edit_fraction),
    EditCV=unlist(lapply(edit_results, function(z){z$cv_bbinom_est}))
  ), by="Sample") %>%
  mutate(FractionalRichness=fractional_richness_beta(Cells*EditFraction/S, EditCV, lib_size=S, outer=FALSE)$Mean)
p <- richness_data %>%
  ggplot(aes(x=Cells, y=FractionalRichness, color=Sample, lty=Sample, group=Sample)) +
    my_theme +
    geom_line(lwd=1.5) +
    theme(legend.title = element_blank(), legend.direction = "vertical") +
    labs(x="Sample Size", y="Edit Fractional Richness") +
    scale_color_paletteer_d("ggsci::nrc_npg")

# Screener's curve
fig_screener <- p +
  my_theme +
  geom_point(
    data=richness_data %>% filter(is.element(Cells, m_screener)),
    aes(x=Cells, y=FractionalRichness),
    size=3
  ) +
  coord_cartesian(xlim=c(NA, 40000), ylim=c(0, 0.45)) +
  theme(legend.position="right") +
  ggtitle("Screener's Curves")
# Selector's curve
fig_selector <- p +
  my_theme +
  scale_x_continuous(trans="log10") +
  geom_point(
    data=richness_data %>% filter(is.element(Cells, 1e6)),
    aes(x=Cells, y=FractionalRichness),
    size=3
  ) +
  coord_cartesian(xlim=c(1e3, NA)) +
  theme(legend.position="right") +
  ggtitle("Selector's Curves")
```

```{r, lib_comparison, fig.width=12, fig.height=7}
(design_fig_lib_comparison[[1]] + edit_fig_lib_comparison[[1]] + fig_screener) /
  (design_fig_lib_comparison[[2]] + edit_fig_lib_comparison[[2]] + fig_selector) +
  plot_annotation(tag_levels = list(c('A','C','E','B','D','F')))
```

Comparative evaluation of two runs of a 10,000 member E. coli library, the runs are named X and Y.  A and B: histogram
and CDF (blue) of design frequencies as determined by deep amplicon sequencing of the reagents.  The red curves
correspond to beta distributions fit by Maximum Likelihood Estimation (MLE).  The estimates for design CV are
`r round(design_results[[1]]$cv_bbinom_est, 2)` and `r round(design_results[[2]]$cv_bbinom_est, 2)` for runs X and Y respectively.
C and D: histogram and CDF (blue) of genomic edit frequences as determined by pWGS.  The red curves are beta distributions
fit by MLE, the shaded area spans the 95% confidence interval for the edit CV estimates.  The estimated edit CVs are 
`r round(edit_results[[1]]$cv_bbinom_est, 2)` and `r round(edit_results[[2]]$cv_bbinom_est, 2)` for runs X and Y respectively.
The pWGS assay is a shallow sampling of edits, with an estimated sampling depth of `r edit_results[[1]]$sampling_depth`
and  `r edit_results[[2]]$sampling_depth` in runs X and Y respectively, which is very small compared to the library
size of 10,000.
The pWGS assay also enables estimation of edit fraction, the estimates are `r round(edit_fraction[[1]], 2)` and
`r round(edit_fraction[[2]], 2)` for runs X and Y.  Run X has a lower edit fraction but also a lower edit CV compared to
run Y, so determination of which run is better to use in downstream applications will depend on the situation.
E: Screener's curves plotting predicted fractional richness against sample size for the two runs.  The points on the curves
correspond to the Screener's scores using the estimated edit fractions.  For a screen of 20,000 or fewer isolates (twice the
library size), run Y is predicted to yield greater fractional richness, with its larger edit fraction making up for its larger
edit CV
F: Selector's curves, like E but with the x-axis expanded to span a range more typical for a selection application.  
The points on the curves annotate the Selector's Score, the predicted fractional richness when sampling 1e6 cells.
The lower edit CV of run X makes it a better choice for a selection application, despite it having less than half the
edit fraction of run Y.

```{r, lib_comparison_extra}
design_fig_lib_comparison[[1]]
edit_fig_lib_comparison[[1]]
fig_screener
design_fig_lib_comparison[[2]]
edit_fig_lib_comparison[[2]]
fig_selector
```
