# Figure 5

```{r, richness_scenarios_setup}
m <- 10^(seq(2,6,length=1000))
f_range <- c(0.15, 0.3, 0.6)
cv_range <- c(0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4)
lib_size <- c(1e2, 1e3, 1e4)
fig_data <- data.frame()
for(S in lib_size) {
  for(f in f_range) {
    for(cv in cv_range) {
      F <- m*f/S
      fig_data <- fig_data %>%
        bind_rows(
          data.frame(
            m=m,
            EditFraction=f,
            FracSampling=F,
	    CV=cv,
            Richness = S*(1-(1+F*cv^2)^(-1/cv^2)),
            LibSize=S
          )
        )
    }
  }
}
fig_a <- fig_data %>%
  filter(EditFraction==0.6 & CV==1.5 & m <= 1e4) %>%
  mutate(LibSize = as.factor(LibSize)) %>%
  ggplot(aes(x=m, y=Richness, group=LibSize, color=LibSize, linetype=LibSize)) +
    my_theme +
    scale_color_paletteer_d("ggsci::nrc_npg") +
    theme(legend.position="none") +
    geom_line(lwd=1) +
    labs(x='Sample Size', y='Edit Richness', color='Library Size', linetype='Library Size')

fig_b <- fig_data %>%
  filter(EditFraction==0.6 & CV==1.5 & m <= 1e4) %>%
  mutate(
    FractionalRichness = Richness/LibSize,
    LibSize = as.factor(LibSize)
  ) %>%
  ggplot(aes(x=m, y=FractionalRichness, group=LibSize, color=LibSize, linetype=LibSize)) +
    my_theme +
    scale_color_paletteer_d("ggsci::nrc_npg") +
    theme(legend.position="right") +
    geom_line(lwd=1) +
    ylim(c(0,1)) +
    labs(x='Sample Size', y='Edit Fractional Richness', color='Library Size', linetype='Library Size')

fig_c <- fig_data %>%
  filter(LibSize==1e3 & EditFraction==0.6 & m >= 1e2) %>%
  mutate(
    FractionalRichness = Richness/LibSize,
    EditFraction = as.factor(EditFraction),
    CV = as.factor(CV)
  ) %>%
  ggplot(aes(x=FracSampling, y=FractionalRichness, group=CV, color=CV, linetype=CV)) +
    my_theme +
    scale_color_viridis(discrete=TRUE, option="viridis") +
    geom_line(lwd=1) +
    ylim(c(0,1)) +
    coord_cartesian(xlim=c(NA,5)) +
    theme(legend.position="none") +
    labs(x='Fractional Sampling', y='Edit Fractional Richness', color='Edit CV', linetype='Edit CV')

fig_d <- fig_c +
  coord_cartesian(xlim=c(NA,NA)) +
  theme(legend.position="right") +
  labs(y="") +
  scale_x_continuous(trans='log10')
```

```{r, richness_scenarios, fig.width=9, fig.height=7}
(fig_a + fig_b) / (fig_c + fig_d) + plot_annotation(tag_levels = 'A')
```
Exploration of richness under the assumption that edit frequencies follow a beta distribution.
**A:** Richness for different library sizes, assuming an edit CV of 1.5 and an edit fraction of 0.6.
**B:** Fractional richness for the same scenarios as used in **A**.
**C:** Screener's curves, showing fractional richness as a function of fractional sampling, with
different values for edit CV.  Fractional sampling is defined as the product of sampling depth and edit
fraction divided by the library size, along with CV it is all that is required to predict fractional
richness under the beta assumption.
**D:** Selector's curves, which are the same figure as **C** with a log-scale x-axis to enable prediction
of fractional richness with the deep sampling that is typically used for a selection experiment.

```{r, richness_scenarios_extra}
fig_a + theme(legend.position="right")
fig_b
fig_c + theme(legend.position="right")
fig_d
```
