# Supplemental Figure 5

```{r, beta_approximations_setup}
fig_data <- expand_grid(
  LibSize=round(10^seq(2, 4, length=200)),
  CV=c(1, 1.5, 2, 2.5, 3.0, 3.5)
) %>%
  mutate(
    BetaA = (LibSize-1)/LibSize/CV^2 - 1/LibSize,
    BetaB = (LibSize-1)*BetaA,
    Error = BetaA*log(BetaB) - lgamma(BetaA+BetaB) + lgamma(BetaB)
  )

fig <- fig_data %>%
  mutate(
    CV = as.factor(CV)
  ) %>%
  ggplot(aes(x=LibSize, y=Error, group=CV, color=CV)) +
    geom_line(lwd=1.5) +
    labs(x = 'Library Size', y = 'Log(Actual/Approximation)') +
    my_theme +
    scale_color_discrete() +
    theme(legend.position="right") +
    scale_x_continuous(trans="log10")
```

```{r, beta_approximations, fig.width=6, fig.height=6}
fig
```
Assessment of accuracy of the approximation of gamma(a+b)/gamma(b) by b^a, for a range
of values relevant to study of edit libraries.  The log ratio of the actual over the approximation
is plotted against library size for a range of different CV values.  The error of the 
approximation is largest when library size is small and CV is large.  The largest log ratio
over the range of parameters evaluated is `r max(fig_data$Error)`, meaning the approximation
is `r sprintf("%1.2f", round(100*(exp(max(fig_data$Error))-1),2))` larger than the actual value,
resulting in the approximation for richness being slightly lower than the exact value.
