# Supplemental Figure 2

```{r, sampling_depth_setup}
fig_data <- expand_grid(
  LibSize=c(1e3, 1e4),
  CV=c(1.5, 2, 2.5),
  Percentile=ppoints(100)
) %>%
  mutate(
    BetaA = (LibSize-1)/LibSize/CV^2 - 1/LibSize,
    BetaB = (LibSize-1)*BetaA,
    Freq = qbeta(Percentile, shape1=BetaA, shape2=BetaB)
  )

fig <- fig_data %>%
  mutate(
    LibSize = as.factor(LibSize),
    CV = as.factor(CV)
  ) %>%
  ggplot(aes(x=Freq, y=Percentile, group=interaction(LibSize, CV), color=CV, linetype=LibSize)) +
    geom_line(lwd=1.5) +
    labs(x = 'Edit Frequency', y = 'CDF', color='Edit CV', linetype='Library Size') +
    my_theme +
    scale_color_discrete() +
    scale_x_continuous(trans="log10")
```

```{r, sampling_depth, fig.width=6, fig.height=6}
fig
```
Cumulative distribution function for edit frequency at a variety of library sizes and CV, assuming
a beta distribution for edit frequency.  Detection of a large fraction of the edits requires very deep
sampling.  For example, in an edit library of size 1000 and with CV of 2, detection of 90%
of the edits would require enough sampling to be able to detect edits at a frequency of 2.6e-7,
and the sampling depth would need to be larger than 1e8, even before factoring in the fraction
of cells that are edited.
